Exact Symbolic Dynamic Programming for Continuous POMDPs

### 2012-10-07 cpomdp/camdp-xadd/doc/MISC/draft1.tex
Reorganizing NIPS12 files

\section{Introduction}
% Write intro here
In many complex systems complete information of the state is not available due to noisy or poor sensors and readings of them. Partially observable Markov Decision Processes (POMDPs)\cite{POMDPfirst} can be used for planning under such uncertainty in abstract problems. In many real-world problems, resources and sensor inputs are naturally modeled using continuous variables.

Unfortunately most POMDP techniques can not be applied to such settings without assuming prior knowledge about the problem domain. Most methods use some approximation to discretize the continuous state, observation or action space which increases computational complexity \cite{Thrun99h}. Exact solutions to a multi-variate continuous state and observation setting has not been approached for the curse of dimensionality problem. In assuming a continuous observation setting, the agent must search for all possible observations that are read from the environment. This can quickly become infeasible even for small problem sizes.

In this paper we provide an exact solution to a subset of POMDPs with continuous states and observations. Our symbolic dynamic programming (SDP) approach assumes discrete noise and piecewise linear dynamics and functions. We formulize our problems using a Discrete and Continuous POMDP (DC-POMDP) model and apply our SDP algorithm. The main problem that rises in any problem modeled using DC-POMDP is the definition of different observation partitions and their probability. We apply symbolic solutions such as integration and maximization to provide an optimal closed-form solution to our problem domains. 
As an example we consider the following power plant example which has mainly been solved in the literature using discrete sets of states and observations~\cite{steam2}. We use the example throughout the paper to help better understand the definitions.

@@

We need to extend the basic SDP framework from \cite{sanner_uai11} by adding continuous observations to the model. The solution to a closed-form value function is similar to the algorithm from \cite{monahan82} apart from the fact that no explicit observation is defined in the continuous case. We redefine the value-iteration algorithm using case representations that are implemented using Extended Algebric decision diagrams (XADD) and provide an efficient automatic way to partition the entire observation space into piecewise linear functions where each partition has a relative probability. We use the univariate \textsc{Power Plant} example to define the main operations and algorithms and also provide empirical results for a multi-variate version of the problem.

@@

 At any of the horizon steps, a DC-POMDP policy $\pi(b)$ is defined as the iterative plan on executing an action and observing all probable outcomes of the set of observations from the $(h-1)$-step. The belief state is updated after this according to the Bayes rule: $\sum_{d_s}\int_{x_s} b(xd_s)T(xd'_s,xd_s,a)Z(xd'_s,xd_o,a)$  where for simiplicity we use ($xd_s = x_s,d_s$) and ($xd_o=x_o,d_o$).
The optimal policy is defined over the belief state as the sum of the expected discounted rewards over horizon $h$ starting with belief $b_0$.
\begin{equation}
V^h_{\Pi^*}(\vec{b}) = E_{\pi^*} \left[ \sum_{h=0}^{H} \gamma^t \cdot r_h \Big| \vec{b}_0 = \vec{b} \right]\nonumber
\end{equation}
%The next section provides the mathematics required to solve this equation in DC-POMDPs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure 1 - policy tree
\begin{figure}[t!]
%\vspace{-1mm}
\begin{center}
\includegraphics[width=0.4\textwidth]{pics/cond_plan2.pdf}
\includegraphics[width=0.45\textwidth]{pics/b1-4.pdf}
\end{center}
\vspace{-2mm}
\caption{\footnotesize Left: Example conditional plan $\beta^h$ for discrete observations. Right: The optimal value function for \textsc{Power Plant}
as a decision diagram: 
the \emph{true} branch is solid, the \emph{false}
branch is dashed.}
\label{fig:cond_plan}
\vspace{-1mm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=0.4\textwidth]{pics/cond_plan2.pdf}
%\end{center}
%\vspace{-3mm}
%\caption{%\footnotesize 
%The optimal value function for \textsc{Power Plant}
%as a decision diagram: 
%the \emph{true} branch is solid, the \emph{false}
%branch is dashed.} 
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Dynamic Programming solution} 
Solving the value function for the optimal policy is performed using Dynamic programming algorithms such as value iteration. 
The decision at each time step is to pick an action based on past actions and observations. The possible set of conditional plans $\beta^h$ correspond to a decision tree. Figure 1 left, shows the decision tree for the simple case of three horizons with discrete observations. It represents a conditional plan consisting of an action and two possible observation strategies. For continuous observations, conditional plans are decision trees with infinitely many branches. In our solution we show that instead of a policy tree with infinite branches, we can create partitions based on relevant observation values, resulting in a policy tree similar to that of figure 1. %From here on we assume this finite set of observation partitioning as $\mathcal{O}$.

@@

Calculating all possible ways of building the value function independent of a certain belief state can define the optimal value function. To derive the $\Gamma$-set of all possible $\alpha$-vectors for each horizon, we use the value iteration algorithm from ~\cite{monahan82}. 
Initializing  $\alpha^0_1 = \vec{0}$ and $\Gamma^0 = \{ \alpha^0_1 \}$, $\Gamma^h$ is obtained from $\Gamma^{h-1}$ using the backup operation defined in (4):\footnote{The $\textrm{\large $\boxplus$}$ of sets is defined as 
$\textrm{\large $\boxplus$}_{j \in \{ 1,\ldots, n \} } S_j = S_1 \textrm{\large $\boxplus$} \cdots \textrm{\large $\boxplus$} S_n$ where the pairwise cross-sum $P 
\textrm{\large $\boxplus$} Q = \{ \vec{p} + \vec{q} | \vec{p} \in P, \vec{q} \in Q \}$.}
\begin{align}
\Gamma^{h}_a   &= r_a + \gamma \textrm{\large $\boxplus$}_{o \in \mathcal{O}} \left\{ g^h_{a,o,j}(\cdot) \right\}_j ;  \forall \alpha^{h-1}_{j} \in \Gamma^{h-1}  \\
\Gamma^h  &= \bigcup_a \Gamma^h_a 
\end{align}
Each action-dependent $\Gamma$ sums over the possible set of $g^h_{a,o,j}(\cdot)$ given an observation model to derive discrete observations $xd_o$ and for all $\alpha^{h-1}_{j} \in \Gamma^{h-1} $. The value $g^h_{a,o,j}(\cdot)$ is computed by summing over all states given the probability functions and previous $\alpha$-vectors.  
For each horizon, the optimal $\alpha$-vector is obtained from the maximum over all $\alpha$-vectors: 
$\alpha^* = \argmax_{\alpha^h_i \in \Gamma^h} \alpha^h_i \cdot b $

@@

Now that we have partitions on the observation space, we only need to multiply the indicators of each case partition in this formula to obtain the probability of each partition such that it sums to one: 
$P(z_k) := \int_{xd_o}\int_{xd_s} P(xd_o|xd'_s,a)*P(xd'_s|xd_s,a)*b_i* \mathbb{I}[\phi_{z_k}] d_{xd_o} d_{xd_s}$
For our example the following holds: 
\begin{align}
P(z_k)=
\begin{cases}
 (2<t_o<6) &: 0.2 \\
(-4<t_o<2) &: 0.6\\
(-8<t_o<-4) &:0.1999
\end{cases} 
\nonumber
\end{align}
Hence we can now use the algorithms and methods of a discrete observation setting using the probabilities of the partitioned observation space. 
%Figure ~\ref{fig:obsPartition} shows the observation partitions obtained in the 1D problem instance for different horizons and their related probabilities. In a lyx file, needed?
Next we present some results for 2-Dimensional continuous observation spaces.

@@

\Begin
{
	$z:=0$;\	
		\For {all $\alpha_j$ in  $\Gamma^{h-1}$}    
		{
    	$\alpha_j(xd_s,xd_o) := \int_{s'} P(xd_{o_i}|xd'_{s_i},a) * P(xd'_{s_i}| xd_{s_i},a)* \alpha_j $;\
		}  
		\For {all $j$ in $\alpha_j(xd_s,xd_o)$}    
		{
		$\delta_{j}(xd_o) := $ $\int_{xd_{s_i}} b_i * \alpha_j(xd_s,xd_o)$\}\ \;
		}
		\For {all $j$ in $\delta_{j}(xd_o)$}    
		{
		$z := max(\delta_j(xd_o),z)$\;
    	}
    	\emph{// $\phi_{z_k}$ logical term on each partition of $z$}\\
   		$P(z_k) := \int_{xd_o}\int_{xd_s} P(xd_o|xd'_s,a)*P(xd'_s|xd_s,a)*b_i* \mathbb{I}[\phi_{z_k}] d_{xd_o} d_{xd_s}$ \;
    \Return{$P(z)$} \;
    %do this for each belief in B
}
\caption{\footnotesize \texttt{GenRelObs}($\Gamma^h,a,b_i$) $\longrightarrow$ $P(z)$ }
\vspace{-1mm}
\end{algorithm}
\decmargin{.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[tbp!]
%\vspace{-2mm}
%\centering
%\includegraphics[width=0.42\textwidth]{pics/nodes.pdf}\\
%\vspace{-2mm}
%\includegraphics[width=0.42\textwidth]{pics/time.pdf}
%\vspace{-2mm}
%\caption{\footnotesize space 
%and time vs. horizon.
%}
%\label{fig:timeSpace}
%\vspace{-4mm}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Empirical Results}
We evaluated our continuous POMDP solution using XADDs on the one-dimensional
\textsc{Power Plant} example and another variant of this problem with two variables. \footnote{
Full problem specifications and Java code to reproduce these experiments are currently 
in Google Code; anonymity restrictions prevent us from providing this link in the submitted paper version.}
We start by defining the 2-dimensional description of this problem:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\vspace{-2mm}
\centering
\includegraphics[width=0.3\textwidth]{pics/time2.pdf}
\includegraphics[width=0.3\textwidth]{pics/nodes2.pdf}
\includegraphics[width=0.3\textwidth]{pics/alpha-vectors2.pdf}
\vspace{-3mm}
\caption{\footnotesize 
{\it (left)} Space vs Horizon; 
{\it (middle)} Time vs Horizon; 
{\it (right)} Number of $\alpha$-vectors vs Horizon.
}
\label{fig:timeSpace}
\vspace{-4mm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf \textsc{2D-Power Plant}:} We consider the more complex model of the power plant similar to \cite{steam2} where the pressure inside the water tank must be controlled to avoid water mixing into the steam or explosion of the tank. We model the pressure variable $p$ as a partially observable variable from the observation readings of the pressure valve $po$. The two actions of increase and decrease are defined based on the change in both the temperature and the pressure. For the increase action the transition functions and the reward function is defined as below: 
\begin{align}
P(p_s'|\vec{p_s},a)&= \delta\left[ p_s' - 
\begin{cases}
 (p+10> 20) &: 20 \\ 
\neq (p+10> 20) &: p_s + 10 \\
\end{cases}
\right]\nonumber
\\
P(t_s'|\vec{t_s},a)&= \delta\left[ t_s' -  t_s +10 \right]\nonumber
\\
R(t_s,p_s,a) &= 
\begin{cases}
(5 \leq p_s \leq 15)\wedge (95 \leq t_s \leq 105)&:50\\
(5 \leq p_s \leq 15)\wedge (t_s \leq 95)&: -1\\
(5 \leq p_s \leq 15)\wedge (t_s \geq 95)&: -3\\				
(p_s \leq 5) &: -3\\						
(p_s \geq 15) &: -5\\ 
\end{cases}\nonumber
\end{align}
There is a high reward for staying withing the safe temperature and pressure range since it produces power, else depending on how safe it is to have values higher or lower than the safe range, penalty is defined.
As for the decrease action, the transition functions reduce the temperature by 5 units and the pressure by 10 units as long as the pressure stays above zero. For the reward function, we assume that there is always a small penalty for decreasing the values because power can not be generated.

For the observation model we consider two continuous uniform distributions such as the following:  
\begin{align}
P(t_o|t_s') &= 
\begin{cases}
 (t_o>t_s + 80) \wedge (t_o<t_s+ 105) &: 0.4 \\
 \neg( (t_o>t_s + 80) \wedge (t_o<t_s+ 105)) &: 0 \\
\end{cases}\nonumber
\end{align}
\begin{align}
P(p_o|p_s') &= 
\begin{cases}
 (p_o>p_s) \wedge (p_o<p_s+10) &: 0.1 \\
 \neg( (p_o>p_s) \wedge (p_o<p_s+10)) &: 0 \\
\end{cases}\nonumber
\end{align}

We define two rectangular uniform beliefs around the regions of rewarding, so that one needs to increase the values while the other should decrease them: 
\begin{align}
b_1 = 
\begin{cases}
(p_o>p_s) \wedge (p_o<p_s+10) \wedge (t_o>t_s+ 90) \wedge (t_o<t_s+ 100)&: 0.01 \\
 \neg( (p_o>p_s) \wedge (p_o<p_s+10) \wedge (t_o>t_s+ 90) \wedge (t_o<t_s+ 100)) &: 0 \\
\end{cases}\nonumber
\end{align}
\begin{align}
b_2 = 
\begin{cases}
(p_o>p_s +10) \wedge (p_o<p_s+30) \wedge (t_o>t_s+ 90) \wedge (t_o<t_s+ 130)&: 0.00125 \\
 \neg((p_o>p_s +10) \wedge (p_o<p_s+30) \wedge (t_o>t_s+ 90) \wedge (t_o<t_s+ 130)) &: 0 
\end{cases}\nonumber
\end{align}
% I can draw this and the 1D belief
In Figure ~\ref{fig:timeSpace}, a time and space analysis of
the two versions of the problem have been performed for up to 6 horizons. Comparing the two problem sizes demonstrates the effect of the number of state-observation variables in our algorithm. As the algorithm progresses, the time required to compute the probability of the partitions and finding the maximum value function increases for both problem sizes and significantly more for the 2D version. The stability in time is due to the fact that each stage almost takes the same time since it has converged quickly.%???
Increase in the problem size, increases the partition numbers on the observation space and this produces more $\alpha$-vectors which also effecting the space required to perform the algorithm. The number of vectors stays the same for most horizons and they drop after convergence in the 2D problem instance. The number of nodes in each iteration increases as more space is required to perform higher iterations.

In Figure ~\ref{fig:3D}  we show plots of the value function for different iterations of the 2D problem instance. Each plot demonstrates the value as a function of the pressure and temperature. Starting with the first iteration, the value is highest for the reward range ($5<p<15 \wedge 95<t<105$) and -1 or less for other places. In the fifth iteration, the value function has partitioned into more pieces showing how higher temperatures can increase the value without considering the effect of the pressure. In the last plot, horizon 6 has better tuned the value function so that higher temperatures and pressures increase the value function and also within the reward range, finer grain partitions have been formed. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% policy2, v2plot.pdf, v9plot
% annotation?
\begin{figure*}[tbp!]
\vspace{-2mm}
\centering
\includegraphics[width=0.31\textwidth]{pics/2d1.pdf}
\includegraphics[width=0.31\textwidth]{pics/2d9.pdf}
\includegraphics[width=0.31\textwidth]{pics/2d111.pdf}
\vspace{-3mm}
\caption{\footnotesize 
{\it (left)} Value function for first iteration; 
{\it (middle)} $V^5(p,t)$; 
{\it (right)} $V^6(p,t)$.
}
\label{fig:3D}
\vspace{-4mm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related Work} 
This work has used the concept of continuous states and the SDP solution to MDPs from ~\cite{sanner_uai11} and continuous observations from the work of \cite{pascalPomdp}. It is exclusive in the sense that it brings together the continuous state and observation POMDPs using a symbolic approach. 
In many applications of the POMDP framework, the state and observation space have been considered as discrete values such as ~\cite{steam2} here we avoid this general simplification and work with the real values from sensors.
%sampling, monte carlo, particle filter, gaussians, perseus, pergeus

There has been prior work on approximate solutions to POMDPs with large or continuous state spaces ~\cite{Thrun99h}, ~\cite{Perseus} and some has been extended to the continuous observation setting using methods such as sampling ~\cite{PerseusObs}.
In most approximate continuous state POMDP work, continuous or large discrete actions has been used. Thus we can extend the current work using \cite{zamaniAAAI} to contain continuous actions and provide exact or approximate solutions.

\section{Conclusion}
We presented the first exact solution to continuous states and observations in a DC-POMDP framework. Transitions and reward functions are defined as piecewise linear functions of the continuous states. Continuous observations require definition of explicit partitions based on the observation model and the belief state of the agent. The key contribution is to define the partitions on the observation space and derive the related probabilities using symbolic integration and maximization. We extend the application to more than one state-observation setting and present the results.

%\subsubsection*{References} 
\bibliography{dcpomdp}
\bibliographystyle{plain}

>>>>

\section{Introduction}
% Write intro here

The following example is used throughout the paper to help better understand the definitions.

@@

Most work in the literature have assumed discretization of the state and observation space ~\cite{steam2}. Here we take a continuous approach using the DC-POMDP framework.

@@

 At any of the horizon steps, a DC-POMDP policy $\pi(b)$ is defined as the iterative plan on executing an action and observing all probable outcomes of the set of observations from the $(h-1)$-step. The belief state is updated after this according to the Bayes rule: $\sum_{d_s}\int_{x_s} b(xd_s)T(xd'_s,xd_s,a)Z(xd'_s,xd_o,a)$  where for simiplicity we use ($xd_s = x_s,d_s$) and ($xd_o=x_o,d_o$).
The optimal policy is defined over the belief state as the sum of the expected discounted rewards over horizon $h$ starting with belief $b_0$.
\begin{equation}
V^h_{\Pi^*}(\vec{b}) = E_{\pi^*} \left[ \sum_{h=0}^{H} \gamma^t \cdot r_h \Big| \vec{b}_0 = \vec{b} \right]\nonumber
\end{equation}
%The next section provides the mathematics required to solve this equation in DC-POMDPs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure 1 - policy tree
\begin{figure}[t!]
%\vspace{-1mm}
\begin{center}
\includegraphics[width=0.4\textwidth]{pics/cond_plan2.pdf}
\includegraphics[width=0.4\textwidth]{pics/cond_plan2.pdf}
\end{center}
\vspace{-2mm}
\caption{\footnotesize Left: Example conditional plan $\beta^h$ for discrete observations. Right: The optimal value function for \textsc{Power Plant}
as a decision diagram: 
the \emph{true} branch is solid, the \emph{false}
branch is dashed.}
\label{fig:cond_plan}
\vspace{-1mm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=0.4\textwidth]{pics/cond_plan2.pdf}
%\end{center}
%\vspace{-3mm}
%\caption{%\footnotesize 
%The optimal value function for \textsc{Power Plant}
%as a decision diagram: 
%the \emph{true} branch is solid, the \emph{false}
%branch is dashed.} 
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Dynamic Programming solution} 
Solving the value function for the optimal policy is performed using Dynamic programming algorithms such as value iteration. 
The decision at each time step is to pick an action based on past actions and observations. The possible set of conditional plans $\beta^h$ correspond to a decision tree. Figure 1 left, shows the decision tree for the simple case of three horizons with discrete observations. It represents a conditional plan consisting of an action and two possible observation strategies. For continuous observations, conditional plans are decision trees with infinitely many branches. In our solution we show that instead of a policy tree with infinite branches, we can create partitions based on relevant observation values, resulting in a policy tree similar to that of figure 1. %From here on we assume this finite set of observation partitioning as $\mathcal{O}$.

@@

Calculating all possible ways of building the value function independent of a certain belief state can define the optimal value function. To derive the $\Gamma$-set of all possible $\alpha$-vectors for each horizon, we use the value iteration algorithm from (Monahan)~\cite{monahan82}. 
Initializing  $\alpha^0_1 = \vec{0}$ and $\Gamma^0 = \{ \alpha^0_1 \}$, $\Gamma^h$ is obtained from $\Gamma^{h-1}$ using the backup operation defined in (4):\footnote{The $\textrm{\large $\boxplus$}$ of sets is defined as 
$\textrm{\large $\boxplus$}_{j \in \{ 1,\ldots, n \} } S_j = S_1 \textrm{\large $\boxplus$} \cdots \textrm{\large $\boxplus$} S_n$ where the pairwise cross-sum $P 
\textrm{\large $\boxplus$} Q = \{ \vec{p} + \vec{q} | \vec{p} \in P, \vec{q} \in Q \}$.}
\begin{align}
\Gamma^{h}_a   &= r_a + \gamma \textrm{\large $\boxplus$}_{o \in \mathcal{O}} \left\{ g^h_{a,o,j}(\cdot) \right\}_j ;  \forall \alpha^{h-1}_{j} \in \Gamma^{h-1}  \\
\Gamma^h  &= \bigcup_a \Gamma^h_a 
\end{align}
Each action-dependent $\Gamma$ sums over the possible set of $g^h_{a,o,j}(\cdot)$ given an observation model to derive discrete observations $xd_o$ and for all $\alpha^{h-1}_{j} \in \Gamma^{h-1} $. The value $g^h_{a,o,j}(\cdot)$ is computed by summing over all states given the probability functions and previous $\alpha$-vectors.  
For each horizon, the optimal $\alpha$-vector is obtained from the maximum over all $\alpha$-vectors: 
$\alpha^* = \argmax_{\alpha^h_i \in \Gamma^h} \alpha^h_i \cdot b $

@@

Now that we have partitions on the observation space, we only need to multiply the indicators of each case partition in this formula to obtain the probability of each partition such that it sums to one: 
$P(z_k) := \int_{xd_o}\int_{xd_s} P(xd_o|xd'_s,a)*P(xd'_s|xd_s,a)*b_i* \mathbb{I}[\phi_{z_k}] d_{xd_o} d_{xd_s}$
For our example the following holds: 
\begin{align}
P(z_k)=
\begin{cases}
 (2<t_o<6) &: 0.2 \\
(-4<t_o<2) &: 0.6\\
(-8<t_o<-4) &:0.1999
\end{cases} 
\nonumber
\end{align}
Hence we can now use the algorithms and methods of a discrete observation setting using the probabilities of the partitioned observation space. Next we present some results for 2-Dimensional continuous observation spaces.

@@

\Begin
{
	$z:=0$;\	
		\For {all $\alpha_j$ in  $\Gamma^{h-1}$}    
		{
    	$\alpha_j(xd_s,xd_o) := \int_{s'} P(xd_{o_i}|xd'_{s_i},a) * P(xd'_{s_i}| xd_{s_i},a)* \alpha_j $;\
		}  
		\For {all $j$ in $\alpha_j(xd_s,xd_o)$}    
		{
		$\delta_{j}(xd_o) := $ $\int_{xd_{s_i}} b_i * \alpha_j(xd_s,xd_o)$\}\ \;
		}
		\For {all $j$ in $\delta_{j}(xd_o)$}    
		{
		$z := max(\delta_j(xd_o),z)$\;
    	}
    	\emph{// $\phi_{z_k}$ logical term on each partition of $z$}\\
   		$P(z_k) := \int_{xd_o}\int_{xd_s} P(xd_o|xd'_s,a)*P(xd'_s|xd_s,a)*b_i* \mathbb{I}[\phi_{z_k}] d_{xd_o} d_{xd_s}$ \;
    \Return{$P(z)$} \;
    %do this for each belief in B
}
\caption{\footnotesize \texttt{GenRelObs}($\Gamma^h,a,b_i$) $\longrightarrow$ $P(z)$ }
\vspace{-1mm}
\end{algorithm}
\decmargin{.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Empirical Results}

\section{Related Work}

\section{Conclusion}

\subsubsection*{References} 
\bibliography{dcpomdp}
\bibliographystyle{plain}
